Prefetching SPARQL query cacher

### 2016-05-26 dissertation/cache-proxy.tex
small

As noted in Section~\ref{sec:implqueryplan}, we rely on rotating joins
to gather triple pattern plans into a larger structure that can be
evaluated together, like a remote SPARQL BGP. On careful inspection, I
found that the join rotation would have had to descend into
great-grandchildren of the top join plan. However, with the IDP
planner, plans are aggressively pruned, and therefore, this
constellation is not considered. This led us (with Gregory Todd
Williams) to conjecture that this weakness is inherit to IDP planning
when using join rotation. We did not attempt to examine this any
further, however.

>>>>

As noted in Section~\ref{sec:implqueryplan}, we rely on rotating joins
to gather triple pattern plans into a larger structure that can be
evaluated together, like a remote SPARQL BGP. On careful inspection, I
found that the join rotation would have had to descend into
great-grandchildren of the top join plan. However, with the IDP
planner, plans are aggressively pruned, and therefore, this
constellation is not considered. This led us (with Gregory Todd
Williams) to conjecture that this weakness is inherit to IDP planning
(and possibly a general problem with any early-pruning planner) 
when using join rotation. We did not attempt to examine this any
further, however.
